### 2024-11-02 paper.qmd
new approach, a model for each subject

The priors were selected based on physiological constraints and are detailed in @eq-priors, ensuring in this way, identifiability of model parameters by constraining the parameter space to physiologically plausible values and ultimately, improving model convergence.

$$
\begin{aligned} 
\alpha &\sim \mathcal{N}(850, 50) \text{ with } \alpha \geq 0 \\
\beta &\sim \mathcal{N}(-400, 50) \text{ with } \beta \leq 0 \\
c &\sim \mathcal{N}(1, 0.2) \text{ with } c \geq 0 \\
\lambda &\sim \mathcal{N}(-3, 3) \text{ with } \lambda \leq 0 \\
\phi &\sim \mathcal{N}(-3, 3) \text{ with } \phi \leq 0 \\
\tau &\sim \mathcal{N}(5, 0.5) \text{ with } \tau \geq 0 \\
\delta &\sim \mathcal{N}(5, 0.5) \text{ with } \delta \geq 0
\end{aligned}
$$ {#eq-priors}

Simulated RRi dynamics based on the prior parameter distributions are shown in [Figure 1](#fig-prior-sim).

@@

The fitting process utilized five Markov Chain Monte Carlo (MCMC) chains, each consisting of 15,000 iterations with a burn-in period of 5,000 iterations, resulting in a total of 50,000 post-warmup samples.

>>>>

To enhance the exploration of parameter space, each subject´s RRi data was standardize against his own mean and standard deviation, improving convergence and an efficient exploration of the posterior distribution in this high dimensional parameter space.

The priors were chosen based on physiological constraints and graphical visualization of standardized RRi data. These priors are detailed in @eq-priors, ensuring in this way, identifiability of model parameters by constraining the parameter space to physiologically plausible values and ultimately, improving model convergence.

$$
\begin{aligned} 
\alpha &\sim \mathcal{N}(1, 0.5) \\
\beta &\sim \mathcal{N}(-2.5, 0.5) \text{ with } \beta \leq 0 \\
c &\sim \mathcal{N}(0.8, 0.2) \text{ with } c \geq 0 \\
\lambda &\sim \mathcal{N}(-2, 0.5) \text{ with } \lambda \leq 0 \\
\phi &\sim \mathcal{N}(-2, 0.5) \text{ with } \phi \leq 0 \\
\tau &\sim \mathcal{N}(5, 0.5) \text{ with } \tau \geq 0 \\
\delta &\sim \mathcal{N}(5, 0.5) \text{ with } \delta \geq 0
\end{aligned}
$$ {#eq-priors}

Simulated standardized RRi dynamics based on prior parameter distributions are shown in [Figure 1](#fig-prior-sim).

@@

The fitting process utilized five Markov Chain Monte Carlo (MCMC) chains, each consisting of 10,000 iterations with a burn-in period of 5,000 iterations, resulting in a total of 25,000 post-warmup samples. The model was fitted for each subject´s standardized RRi data, allowing the estimation of the model parameters associated with individual RRi dynamics for each subject. Afterwards, we transformed back to the RRi scale the $\alpha$ and $\beta$ parameters, ensuring a physiologically meaningful interpretation of model estimation.
